<<<<<<< HEAD
---
title: "My Personal Statement"
---
<link rel="stylesheet" href="style.css" >

I was born in a small town called 弋阳 in Jiangxi, China.Growing up being the only child in a loving family, my parents supports me in every way they possibly can. Thank you dad and mom for always believing in me and for your unconditional love. (In the bottom of this page is a pinned map of my hometown *Yiyang* )

In Fall, 2009, I came to University of Kentucky for college and earned my B.S.degree in mathematics 
in 2012. As much as I enjoy mathematics, I am also really drawn to medicine. I knew I want an career in healthcare, but I was confused to where in medicine would be a good fit for me. I am an enthusiast reader and read many books by [Dr. Atul Gawande](http://atulgawande.com/). His books *Better*， *Being Mortal* really inspired me to look deep into a field in medicine where I can help discover new things and better patient care. And the term biostatistics came up.

To me, biostatistics is the pefect intersection of mathematics and medicine. I was lucky enought to talk to a professor of mine who took the time to connect me with someone he knows that works as a Biostatistician in a pharmaceutical company. She explaines in detail what a career as a M.S. biostatistician entails. With that information, I went to study in Rutgers Univerisy and later graduated with a M.S. degree in Biostatistics. 

Graduated top of my class, I was sure I am ready for whatever challenges work throw at me. I was ready to use data to help researchers test their hypothesis. And I was wrong. Three years and two jobs later, I can say I am learning new things about statistics and medicine everyday. My understanding of biostatistics has been deepened through many informative research activities. 

























```{r, include=FALSE}

library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=117.43, lat=28.42, popup="The birthplace of me")

```

```{r echo=FALSE, fig.width=4, fig.align='center', fig.height=4, message=FALSE, warning=FALSE}
m  # Print the map
```


=======
---
title: "My Personal Statement"
---
<link rel="stylesheet" href="style.css" >

I was born in a small town called 弋阳 in Jiangxi, China.Growing up being the only child in a loving family, my parents supports me in every way they possibly can. Thank you dad and mom for always believing in me and for your unconditional love. (In the bottom of this page is a pinned map of my hometown *Yiyang* )

In Fall, 2009, I came to University of Kentucky for college and earned my B.S.degree in mathematics 
in 2012. As much as I enjoy mathematics, I am also really drawn to medicine. I knew I want an career in healthcare, but I was confused to where in medicine would be a good fit for me. I am an enthusiast reader and read many books by [Dr. Atul Gawande](http://atulgawande.com/). His books *Better*， *Being Mortal* really inspired me to look deep into a field in medicine where I can help discover new things and better patient care. And the term biostatistics came up.

To me, biostatistics is the pefect intersection of mathematics and medicine. I was lucky enought to talk to a professor of mine who took the time to connect me with someone he knows that works as a Biostatistician in a pharmaceutical company. She explaines in detail what a career as a M.S. biostatistician entails. With that information, I went to study in Rutgers Univerisy and later graduated with a M.S. degree in Biostatistics. 

Graduated top of my class, I was sure I am ready for whatever challenges work throw at me. I was ready to use data to help researchers test their hypothesis. And I was wrong. Three years and two jobs later, I can say I am learning new things about statistics and medicine everyday. My understanding of biostatistics has been deepened through many informative research activities. 

























```{r, include=FALSE}

library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=117.43, lat=28.42, popup="The birthplace of me")

```

```{r echo=FALSE, fig.width=4, fig.align='center', fig.height=4, message=FALSE, warning=FALSE}
m  # Print the map
```


>>>>>>> b55c26c792a9360c3b218334c95a7a453d2ba286
